Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-04-24 Manuscript.Rmd
new revisions, including switching from DMN to DN, abstract, and intro

---
title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
  word_document: 
    reference_docx: APA_style.docx #Style_reference_draft.docx 
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}

@@

# produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
metaPerm <- function(list1 = studyList_sv, list2 = studyList_dmn, labels = Yeo_labels, perm = 1) {

@@

  # combine study lists
  allStudies <- c(studyList_sv, studyList_dmn)

  # Sample all the studies and divide into 2 groups
  randPerm <- sample(allStudies)
  tmpSV <- randPerm[seq(length(list1))]
  tmpDMN <- randPerm[-seq(length(list1))]

  # Count the number of times each region was reported in the literature
  tmpDF <- data.frame(Parcel = gsub("_", "", labels),
                      SV = sapply(labels, function(roi) {length(grep(roi, tmpSV))}),
                      DMN = sapply(labels, function(roi) {length(grep(roi, tmpDMN))}))

  # Perform the prop test for each pair and get the max chi-squared stat
  maxStat <- max(
    apply(tmpDF[, 2:3], 1, function(data) {
      prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
    }
    ), na.rm = T)

@@

## get ROI coords & index
# The point here is to reduce the summary dframes from community detection to show only ROIs
# Should work for extracting any label-indexed dframe though
# I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){

@@

# Ensure that all spectral communities associated with 7m (i.e. DMN) have the same label value of 1 
evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {

@@

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){

@@

# Perform pairwise comparisons of clustering outcomes on all subjects
comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
  # Alternatively, if a second MOI is added 
  # Inputs
  # 
  # Data: the list of summaries produced by the script
  # 
  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
  # 
  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation
  # ARI can yield many decimals, thus inflating the ratios. I thus round at 4 decimals.

@@

# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
# The threshold will be based on proportion DMN given by thresholdRange
threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {

  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
  # get the 2 values with highest reports (this should be stable upper/lower proportions)
  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
  stableExtremes <- sort(as.numeric(names(stableExtremes)))

@@

  # Iterate over the possible FV until DMN affiliations go below 1%
  count <- 1
  while (meanProp >= thresholdRange[1]) {

    # get the mean proportion of DMN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))

@@

  # Iterate over the possible FV until DMN affiliations go over 99%
  count <- 1
  while (meanProp <= thresholdRange[2]) {

    # get the mean proportion of DMN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))

@@

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
# this is used to get the number of subjects 
setwd('./Summary/')
nSubj <- length(dir())
```

@@

  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making. The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC). At the same time, differences between the two sets of activation patterns are not apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n = 100 from the Human Connectome Project). We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region. The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day). The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC. Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.

**Keywords:** brain networks; DMN; individual differences

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018]. One such function is subjective valuation during economic decision making [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued. These regions are also implicated in a set of functions associated with the default-mode network (DMN). DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].

  Coordinate-based meta-analyses of the fMRI literature suggest that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017]. The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN. Within PCC and adjacent precuneus, a more posterior subregion appears DMN-specific, whereas a more anterior subregion is implicated in both effects. One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects. The potential existence of common nodes has prompted theories positing overlap between valuation and DMN-related cognitive processes. For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].

  However, concluding that colocalization at the group level equates to overlap in cognitive function requires a better understanding of individual-level heterogeneity in topographic patterns of brain activity. A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015; @Tobyne2018], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018b; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DMN effects within mPFC and PCC.

  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e. time-series correlations between pairs of locations in the brain). Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017; @Smith2009]. A popular way to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a]. In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017]. Such communities represent clusters of network nodes that share more connections with each other than with the rest of the network [@Fortunato2016]. In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN. Spectral partitioning (SP) is an efficient community detection algorithm that deterministically forces such bisections [@Fiedler1975; @Belkin2003]. For a network composed of pairwise correlations among its nodes, SP partitions the network by binarizing the eigenvector linked to the second-to-lowest eigenvalue of the adjusted (Laplacian) correlation matrix according to its sign (i.e. positive or negative number). SP has recently been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019]. This method can therefore capture a refined group of brain regions that more cohesively share spontaneously covarying temporal activation patterns during rest.

  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community. The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles. Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we provide evidence that the resulting automatically defined communities resembled an organizational scheme recently observed in a series of low N studies [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

For all analyses, we defined our search space based on the 17-network parcellation proposed by Yeo et al. [-@Yeo2011]. First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k). Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions. This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1). The search space was naturally divided into two spatially discontinuous clusters that covered PCC and mPFC, facilitating the study of each general region separately.

@@

We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DMN effects. For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013]. For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009]. These coordinates represent the areas that exceeded the statistical significance threshold in each original study. For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009]. The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/). **TODO: The Glasser et al. (2016) parcellation was resampled to fsaverage to pair spheres to parcels from our search space**. Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel. Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.

With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other with a chi-squared test. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains. This gave us a null distribution of 5000 maximum chi-squared values. The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.

@@

Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points (14 min 24 s) for a total of 4800 time points. Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used. See [@VanEssen2012] for more details about the data acquisition protocol.

@@

Where $I$ is an identity matrix of size $n$, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its Fisher transformed correlation values with every other vertex), and $W$ is the Fisher transformed network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975]. This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis. The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

@@

To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 99% of the time.

@@

setwd('../DMN/')
templist <- dir()
studyList_dmn <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count
nRegions_dmn <- do.call(rbind, studyList_dmn) %>% count
nRegions_all <- left_join(nRegions_sv, nRegions_dmn, by = "X1")

@@

# concatenate all proportion of DMN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
allPropDMN <- sapply(Summaries, "[[", "slidePropDMN")

>>>>

---
title: 'Individual heterogeneity in the functional network topography of the medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
  word_document: 
    reference_docx: APA_style.docx #Style_reference_draft.docx 
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r Libraries and functions, include = FALSE, echo = FALSE}

@@

# produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {

@@

  # combine study lists
  allStudies <- c(studyList_sv, studyList_DN)

  # Sample all the studies and divide into 2 groups
  randPerm <- sample(allStudies)
  tmpSV <- randPerm[seq(length(list1))]
  tmpDN <- randPerm[-seq(length(list1))]

  # Count the number of times each region was reported in the literature
  tmpDF <- data.frame(Parcel = gsub("_", "", labels),
                      SV = sapply(labels, function(roi) {length(grep(roi, tmpSV))}),
                      DN = sapply(labels, function(roi) {length(grep(roi, tmpDN))}))

  # Perform the prop test for each pair and get the max chi-squared stat
  maxStat <- max(
    apply(tmpDF[, 2:3], 1, function(data) {
      prop.test(data, c(length(tmpSV), length(tmpDN)))$statistic
    }
    ), na.rm = T)

@@

## get ROI coords & index
# The point here is to reduce the summary dframes from community detection to show only ROIs
# Should work for extracting any label-indexed dframe though
# I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
getCoords <- function(Labels = DN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){

@@

# Ensure that all spectral communities associated with 7m (i.e. DN) have the same label value of 1 
evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {

@@

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = DNval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){

@@

# Perform pairwise comparisons of clustering outcomes on all subjects
comparePartitions <- function(Data = DNval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
  # Alternatively, if a second MOI is added 
  # Inputs
  # 
  # Data: the list of summaries produced by the script
  # 
  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
  # 
  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation
  # ARI can yield many decimals, thus inflating the ratios. I thus round at 4 decimals.

@@

# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
# The threshold will be based on proportion DN given by thresholdRange
threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {

  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
  # get the 2 values with highest reports (this should be stable upper/lower proportions)
  stableExtremes <- sort(table(Data$slidePropDN), decreasing = T)[seq(2)]
  stableExtremes <- sort(as.numeric(names(stableExtremes)))

@@

  # Iterate over the possible FV until DN affiliations go below 1%
  count <- 1
  while (meanProp >= thresholdRange[1]) {

    # get the mean proportion of DN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDN))

@@

  # Iterate over the possible FV until DN affiliations go over 99%
  count <- 1
  while (meanProp <= thresholdRange[2]) {

    # get the mean proportion of DN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDN))

@@

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are implicated in multiple cognitive functions, including subjective valuation processes and processes linked to the default network (DN). Our ability to interpret these seemingly co-localized effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DN effects relative to valuation. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project). The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable across test/retest sessions and varied markedly across individuals, especially in mPFC. Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions.

**Keywords:** brain networks; DN; individual differences

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018]. One such function is subjective valuation during economic decision making. Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. These regions are also implicated in a set of functions associated with the default-mode network (DN). DN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].

  Coordinate-based meta-analyses of the fMRI literature show that valuation and DN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017]. The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DN. Within PCC and adjacent precuneus, a more posterior subregion appears DN-specific, whereas a more anterior subregion is implicated in both effects. One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DN effects. The potential existence of common brain nodes has prompted theories positing psychological overlap between valuation and DN-related processes. For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013a]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC.

  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e. BOLD time-series correlations between pairs of locations in the brain). Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Smith2009; @Tobyne2017]. A functional connectome can be represented in the form of a network, and graph theoretic methods can be applied to analyze the network's structure [@Bassett2017; @Rubinov2010]. In the context of network analysis, community detection algorithms subdivide brain networks into sets of nodes that share more connections with each other than with the rest of the network [@Fortunato2016; @Garcia2017]. Here we use the technique of spectral partitioning (SP), an efficient community detection algorithm that deterministically subdivides a network into two communities [@Belkin2003; @Chung1999; @Fiedler1975]. SP has been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019]. We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns during rest.

  In this study, we aimed to subdivide regions commonly attributed to both DN and subjective valuation into individual-specific DN and non-DN communities, and to quantify the degree of topographic heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community. The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles. Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities aligns with a recently proposed scheme for the organization of DN subdivisions. [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

For all analyses, we defined our search space based on the 17-network parcellation proposed by Yeo et al. [-@Yeo2011]. First, we selected vertices on the cortical surface that were contained by the DN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k). Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions. This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1). The search space was naturally divided into two spatially discontinuous clusters that covered PCC and mPFC, facilitating the study of each general region separately.

@@

We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN effects. For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013]. For DN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009]. These coordinates represent the areas that exceeded the statistical significance threshold in each original study. For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009]. The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/). **TODO: The Glasser et al. (2016) parcellation was resampled to fsaverage to pair spheres to parcels from our search space**. Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel. Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.

With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other with a chi-squared test. We permuted the label of every study (i.e. DN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains. This gave us a null distribution of 5000 maximum chi-squared values. The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.

@@

Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r length(dir(path = './Summary'))`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points (14 min 24 s) for a total of 4800 time points. Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used. See [@VanEssen2012] for more details about the data acquisition protocol.

@@

Where $I$ is an identity matrix of size $n$, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its Fisher transformed correlation values with every other vertex), and $W$ is the Fisher transformed network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975]. This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis. The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

@@

To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DN or non-DN more than 99% of the time.

@@

setwd('../DN/')
templist <- dir()
studyList_DN <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count
nRegions_DN <- do.call(rbind, studyList_DN) %>% count
nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")

@@

# concatenate all proportion of DN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
allPropDN <- sapply(Summaries, "[[", "slidePropDN")
